%!TEX TS-program = xelatex
\documentclass[]{resume-class}

\begin{document}`
\header{Cory Ginsberg}
       {cory.ginsberg1@gmail.com \textbullet \hspace{0.01cm} (847) 494 - 0910}
       {coryginsberg.com \textbullet \hspace{0.01cm} github.com/coryginsberg}

\section{Education}
    \begin{entrylist}
        \entry
            {2014 - June 2018}
            {Bachelor of Science}
            {DePaul University}
            {Computer Science}
    \end{entrylist}


\section{Technical Summary}
    \begin{entrylist}
        \entry
            {Known Languages}
            {Swift, Objective-C, Java, Python\\CSS, HTML, JavaScript/TypeScript\\ C, SQL, TeX/LaTeX}
            {}
            {}
        \entry
            {Known Software}
            {Photoshop, Illustrator, After Effect\\Maya, SQLDeveloper, IntelliJ IDEA} % !!Only put the last ones on resumes that are going to gaming companies!! %
            {}
            {}
    \end{entrylist}

\section{Programming Experience}
    \begin{entrylist}
        \entry
            {iOS/Android App}
            {Assurance HVAC}
            {}
            {Allows customers to call Assurance HVAC quickly in an emergency, get coupons, and find out what area the company covers.}
        \entry
            {Website}
            {Breathe EZ Home Solutions}
            {breatheezhome.com}
            {Allows customers to get coupons, request service, and view more information about the company online.}
    \end{entrylist}

\section{Internship Experience}

    \begin{entrylist}
        \entry
            {May - August 2012}
            {Intern}
            {Entec Data Managers, Inc.}
            {Learned how a database system works on the inside.\\
            Used Microsoft Access to build/maintain databases.\\
            Learned VBA, SQL, and Visual Basic .NET while interning.}
    \end{entrylist}

\section{Work Experience}

    \begin{entrylist}
        \entry
            {2016 - Present}
            {Student Center Student Manager}
            {DePaul University}
            {Assist crew members with setting up and assisting events, as well as answering any and all questions guests have and reporting on the activities of crew members.}
        \entry
            {2015 - 2016}
            {Student Center Crew Member}
            {DePaul University}
            {Assist guests with any and all requests, as well as seting up and assisting events for said guests.}
        \entry
            {2012 - 2015}
            {Lifeguard}
            {Vernon Hills Park District}
            {Watch out for the wellbeing of guests, as well as prepare the pool for the demands of the guests.
             Lifeguards are responsible for teaching swimming lessons in addition to guarding the pool.}
    \end{entrylist}

\end{document}
